{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-04 Paper/main.tex

\begin{document}
	\title{{\LARGE Model Selection for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}}
	\author{Jonghun Baek, Jakob R. Juergens, Jonathan Willnow}
	\date{11.02.2022}
	\maketitle
	\vspace{1.5 cm}
	\begin{center}
		Research Module in Econometrics and Statistics \\
		Winter Semester 2021/2022
	\end{center}

@@

@@

>>>>

\begin{document}
	\title{{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}}
	\author{Jonghun Baek, Jakob R. Juergens, Jonathan Willnow}
	\date{11.02.2022}
	\maketitle
	\vspace{1.5 cm}
	\begin{center}
		Research Module in Econometrics and Statistics \\
		Winter Semester 2021/2022
	\end{center}

@@

	The performance of this estimation procedure depends in part on the quality of the approximation in Equation \ref{simplified_model_basis_equation}. Therefore, it is interesting to think about when the approximation error is small... {\color{red}Continue Here Jakob!!!}

@@

	As in the previous case, the performance of this estimation depends the quality of the approximation made during the derivation of this estimator. Therefore, it is interesting to think about when these errors are small... {\color{red}Continue Here Jakob!!!}
